New lower bounds for Schur and weak Schur numbers

### 2021-04-14 article/article.tex
anglais
modification organisation generale

This paper provides new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction
to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\). 
We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former 
works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions 
into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
imposing certain conditions on the good 5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
\(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).

@@

\include{intro.tex}

@@

\appendix
\renewcommand{\arraystretch}{1}

\section{SF-templates}

\begin{center}
SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
\begin{tabular}{|*{2}{c|}}
	\hline
	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
	\hline
	2 & 2, 5, 14, 15, 25, 26 \\
	\hline
	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
	\hline
	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
	\hline
\end{tabular}
\end{center}

\begin{center}
SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
\begin{tabular}{|*{2}{c|}}
	\hline
	1 & 1, 5, 18, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103 \\
	 & 106, 110 \\
	\hline
	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54 \\
	& 101, 104, 109 \\
	\hline
	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55 \\
	& 100, 107, 108 \\
	\hline
	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
	\hline
	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
	\hline
\end{tabular}
\end{center}

\begin{center}
SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
\begin{tabular}{|*{2}{c|}}
	\hline
	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
	\hline
	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
	\hline
	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
	\hline
	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79\\
	& 84, 95, 98, 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155\\
	& 156, 159, 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374\\
	& 378\\
	\hline
	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75\\
	& 76, 77, 80, 81, 83, 85, 86, 87, 90, 93, 94, 97, 105, 189, 196\\
	& 197, 200, 203, 206, 207, 209, 214, 219, 231, 298, 310, 315, 320, 322, 323\\
	& 326, 329, 332, 333, 340\\
	\hline
	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301\\
	& 302, 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318\\
	& 319, 321, 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355\\
	& 356, 363, 380\\
	\hline

\end{tabular}
\end{center}

\section{WSF-templates}

\begin{center}
WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
\begin{tabular}{|*{2}{c|}}
	\hline
	1 & 1, 2, 4, 8, 11, 22, 25, \(\mathbf{(N+1)}\)\\
	\hline
	2 & 5, 6, 7, 19, 21, 23, 36\\
	\hline
	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
	\hline
	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40\\
	& 41, 42\\
	\hline
\end{tabular}
\end{center}

This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.

>>>>

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
Rowley's "templates"-based approach for Ramsey and Schur numbers. Finding suitable templates allows us to apply Rowley's construction
to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\). 
We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former 
works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions 
into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
\(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).

@@

\include{introduction.tex}

\include{state_of_the_art.tex}

\include{definitions_notations.tex}

@@

\include{appendix.tex}
